A Two-Infall Star Formation History with Outflows and Radial Migration

### 2025-02-11 src/tex/ms.tex

\begin{figure}
    \centering
    \includegraphics{figures/onezone_sfe_hiatus.pdf}
    \caption{Caption.}
    \label{fig:onezone-sfe-hiatus}
\end{figure}

@@

>>>>

@@

\subsection{Star Formation Hiatus}
\label{sec:sfe-hiatus}

The two-infall model falls into the broader category of GCE models which reproduce the $\alpha$-bimodality by halting or severely limiting star formation for some duration. For the two-infall model, this phase of low star formation immediately precedes the second infall epoch and is due to the relatively short timescale of the first infall epoch. However, as we have shown, the dilution of the ISM resulting from the second infall poses a challenge when comparing to age--abundance data.

A bursty infall history is not the only way to produce a gap in the star formation history. \citep{beane_rising_2024} present

\begin{figure}
    \centering
    \includegraphics{figures/onezone_sfe_hiatus.pdf}
    \caption{Abundance tracks and distributions from one-zone models which experience an efficiency-driven starburst. The blue dashed curve represents the fiducial model that has an exponentially declining infall rate and constant star formation efficiency timescale $\tau_\star=2$ Gyr. The red solid curve plots the output of a model which experiences an enhancement of $\tau_\star$ by a factor of 10, for a duration of 200 Myr, starting at $t=1.4$ Gyr. The greyscale histogram presents the number density of APOGEE stars in [O/Fe]--[Fe/H] space, and the gray histograms in the marginal panels show the APOGEE stellar abundance distributions.}
    \label{fig:onezone-sfe-hiatus}
\end{figure}
